---
title: "Statistical methods for archaeological<br>data analysis I: Basic methods"
author: "Martin Hinz"
date: "FS 2019"
institute: "Institut für Archäologische Wissenschaften, Universität Bern"
output:
  xaringan::moon_reader:
    keep_md: true
    chakra: libs/remark-latest.min.js
    css: ["libs/default.css", "libs/default-fonts.css", "libs/customize.css"]
    lib_dir: libs
    seal: false
    nature:
      beforeInit: "libs/macros.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      fig_caption: yes
---
class: title-slide
```{r, echo = FALSE}
# https://stackoverflow.com/questions/25646333/code-chunk-font-size-in-rmarkdown-with-knitr-and-latex
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

```{r, echo = FALSE, results="asis"}
cat('## ', rmarkdown::metadata$title)
```
.small[
```{r, echo = FALSE, results="asis"}
cat('#### ', rmarkdown::metadata$author)
```

```{r, echo = FALSE, results="asis"}
cat(rmarkdown::metadata$institute)
```

```{r, echo = FALSE, results="asis"}
cat(rmarkdown::metadata$date)
```

### Presentations

- [01. Session: Introduction](01_session/session_1_introduction.html) | 20.02.2019
- [02. Session: Introduction into R](02_session/session_2_intro_R.html) | 27.02.2019
- [03. Session: Explorative Statistics/Graph. Display](03_session/session_3_exp_graph.html) | 20.03.2019
- [04. Session: Descriptive Statistics](04_session/session_4_descr_stat.html) | 27.03.2019
- [05. Session: Nonparametric Tests](05_session/session_5_nonpara_tests.html) | 03.04.2019
- [06. Session: Chi-square test](06_session/session_6_chi_squared_test.html) | 10.04.2019
- [07. Session: Probability Theory and Distributions](07_session/session_7_probability_theory.html) | 01.05.2019
- 08\. Session: Distributions | no date
- [09\. Session: Parametric Tests](09_session/session_09_parametric_tests.html) | 08.05.2019
- [10\. Session: Regression & Correlation](10_session/session_10_regression_correlation.html) | 15.05.2019
- [11\. Session: Cluster Analysis](11_session/session_11_cluster_analysis.html) | 22.05.2019
- [12\. Session: Correspondence Analysis](12_session/session_12_correspondence_analysis.html) | 29.05.2019

]

.footnote[
.small[
<sup>\*</sup> You can find the **code of this presentations** at the [github repository](https://github.com/MartinHinz/smada_I_2019). You might also like to check out the **video tutorials** in [english](https://tube.switch.ch/channels/b191ef92) or [german](http://vitutr.archaeological.science/).
]
]